The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-18 src/ms.tex
fix graphicspath because of syw incompatibility

% To allow putting figures in a subdir
\graphicspath{{figures/}}

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=\textwidth]{python-mentions.pdf}
        \caption{
            Yearly full-text mentions of programming languages (indicated in the
            figure legend) in refereed publications in the astronomical
            literature database in the Astrophysics Data System (ADS).
            \python has rapidly become the dominant programming language
            mentioned in refereed articles over the last 10 years.
        }
        \label{fig:python-mentions}
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.9\textwidth]{Ncommitters_vs_frac_commits.pdf}
        \caption{
            The cumulative fraction of Git commits to the \astropypkg core
            package as a function of number of contributors (committers) broken
            into three equal-length time periods between the start of \astropypkg
            and the feature freeze date of v5.0.
            The time eras early, mid, and recent correspond to the approximate
            year ranges 2011--2015, 2015--2018, 2018--2021 (defined more
            precisely in Section~\ref{sec:project-contributors}).
            In all eras, the majority of commits to the \astropypkg core package
            have come from a small subset of the total number of contributors.
            For example, as annotated in the figure, 90\% of the Git commits
            have come from 18, 34, and 44 committers in the early, mid, and
            recent eras, respectively.
        }
        \label{fig:contributor-summary:Ncommitters}
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.75\textwidth]{top_contributors_career.pdf}
        \caption{
            The career stages and/or positions of the top contributors within
            each time era (defined as having contributed $>50$ commits to the
            \astropypkg core package in each era).
            The time eras early, mid, and recent correspond to the approximate
            year ranges 2011--2015, 2015--2018, 2018--2021 (defined more
            precisely in Section~\ref{sec:project-contributors}).
        }
        \label{fig:contributor-summary:top}
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.75\textwidth]{commits_committers_per_month.pdf}
        \caption{
            \textbf{Top panel:} The number of Git commits per month (defined as
            consecutive 30 day windows) merged into the \astropypkg core
            package over the whole history of the Project (up to end of 2021,
            v5.0).
            The dark line shows the mean rate using a 1 year rolling window, but
            the under-plotted gray line shows the raw monthly rate.
            The raw number clearly peaks just before feature freezes (vertical
            lines) as a flurry of activity leading up to each release, but in
            recent years the mean rate has remained steady at about $\sim$300
            commits per month.
            \textbf{Bottom panel:} Similar to above, but now showing the number
            of unique Git committers who contribute to the \astropypkg core
            package each month (again defined as consecutive 30 day windows).
            While this also shows some variation depending on proximity to
            feature freezes, in recent years the mean rate of unique
            contributors has remained consistent at about $\sim$22 committers
            per month.
        }
        \label{fig:contributor-summary:per-month}
    \end{centering}
\end{figure}

@@

\begin{figure}[th!]
  \begin{centering}
    \includegraphics[width=\textwidth]{docu_analytics.pdf}
      \caption{
          The number of users who accessed the \astropypkg core package
          documentation in 2021, based on data from Google Analytics.
          The circle markers show the approximate locations of home institutions
          for \astropy voting members (green) and coordination committee members
          (red), demonstrating the over-representation of the United States and,
          less so, Europe given the global spread of \astropypkg users.
      }
      \label{fig:User-analytics-locations}
  \end{centering}
\end{figure}

>>>>

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=\textwidth]{figures/python-mentions.pdf}
        \caption{
            Yearly full-text mentions of programming languages (indicated in the
            figure legend) in refereed publications in the astronomical
            literature database in the Astrophysics Data System (ADS).
            \python has rapidly become the dominant programming language
            mentioned in refereed articles over the last 10 years.
        }
        \label{fig:python-mentions}
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.9\textwidth]{figures/Ncommitters_vs_frac_commits.pdf}
        \caption{
            The cumulative fraction of Git commits to the \astropypkg core
            package as a function of number of contributors (committers) broken
            into three equal-length time periods between the start of \astropypkg
            and the feature freeze date of v5.0.
            The time eras early, mid, and recent correspond to the approximate
            year ranges 2011--2015, 2015--2018, 2018--2021 (defined more
            precisely in Section~\ref{sec:project-contributors}).
            In all eras, the majority of commits to the \astropypkg core package
            have come from a small subset of the total number of contributors.
            For example, as annotated in the figure, 90\% of the Git commits
            have come from 18, 34, and 44 committers in the early, mid, and
            recent eras, respectively.
        }
        \label{fig:contributor-summary:Ncommitters}
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.75\textwidth]{figures/top_contributors_career.pdf}
        \caption{
            The career stages and/or positions of the top contributors within
            each time era (defined as having contributed $>50$ commits to the
            \astropypkg core package in each era).
            The time eras early, mid, and recent correspond to the approximate
            year ranges 2011--2015, 2015--2018, 2018--2021 (defined more
            precisely in Section~\ref{sec:project-contributors}).
        }
        \label{fig:contributor-summary:top}
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.75\textwidth]{figures/commits_committers_per_month.pdf}
        \caption{
            \textbf{Top panel:} The number of Git commits per month (defined as
            consecutive 30 day windows) merged into the \astropypkg core
            package over the whole history of the Project (up to end of 2021,
            v5.0).
            The dark line shows the mean rate using a 1 year rolling window, but
            the under-plotted gray line shows the raw monthly rate.
            The raw number clearly peaks just before feature freezes (vertical
            lines) as a flurry of activity leading up to each release, but in
            recent years the mean rate has remained steady at about $\sim$300
            commits per month.
            \textbf{Bottom panel:} Similar to above, but now showing the number
            of unique Git committers who contribute to the \astropypkg core
            package each month (again defined as consecutive 30 day windows).
            While this also shows some variation depending on proximity to
            feature freezes, in recent years the mean rate of unique
            contributors has remained consistent at about $\sim$22 committers
            per month.
        }
        \label{fig:contributor-summary:per-month}
    \end{centering}
\end{figure}

@@

\begin{figure}[th!]
  \begin{centering}
    \includegraphics[width=\textwidth]{figures/docu_analytics.pdf}
      \caption{
          The number of users who accessed the \astropypkg core package
          documentation in 2021, based on data from Google Analytics.
          The circle markers show the approximate locations of home institutions
          for \astropy voting members (green) and coordination committee members
          (red), demonstrating the over-representation of the United States and,
          less so, Europe given the global spread of \astropypkg users.
      }
      \label{fig:User-analytics-locations}
  \end{centering}
\end{figure}
